\newcommand{\sectionRepos}{
\section*{FEATURED PERSONAL PROJECTS}

\textbf{mercury\_strategies} [Private Repository] (work in progress)
\begin{itemize}
    \item \academicversion{Engineered a platform-agnostic trading system for weather-derivative prediction markets (e.g., Polymarket) using an asynchronous event-bus architecture in Python. Implemented a watcher-based service for real-time polling of weather providers and high-frequency market state through WebSockets and local orderbook monitoring; deployed dockerized on AWS for 24/7 automated operation.}\industryversion{Developed an event-driven engine for capturing alpha in weather-derivative prediction markets (Polymarket), managing a dockerized infrastructure on AWS with integrated risk management. Features a provider-agnostic collection and analysis layer, asynchronous watcher architecture for real-time signal generation, and automated execution with velocity rotation, local orderbook tracking, and risk-aware position sizing via the Kelly Criterion. Includes 4 months of manual prediction market trading to gain market knowledge, intuition, and experience.}
\end{itemize}

\vspace{0.5em}

\textbf{quant\_core} (\url{https://github.com/kyleyhw/quant_core})
\begin{itemize}
    \item \academicversion{Architected a market-agnostic algorithmic trading framework using a Market Adapter pattern to decouple core logic from broker-specific APIs. Implemented a quantitative pipeline for time-series forecasting and regime detection using Hidden Markov Models (HMM) and XGBoost.}\industryversion{Developed an open-core algorithmic trading platform with a flexible, modular architecture for strategy development and automated execution via Interactive Brokers (IBKR). Features a comprehensive backtesting engine with high-efficiency data caching and integrated risk management.}
\end{itemize}

\vspace{0.5em}

\academicversion{\textbf{sound\_simulation} (\url{https://github.com/kyleyhw/sound_simulation})
\begin{itemize}
    \item A numerical simulation of physical waves in N-dimensions, implemented in Python. The simulation allows for the creation of physical boundaries and obstacles, and models their interaction with the waves. Future work aims to use this simulation to generate training data for machine learning models.
\end{itemize}}
\industryversion{\textbf{agent\_evolve} (\url{https://github.com/kyleyhw/agent-evolve})
\begin{itemize}
    \item Created a multi-model, cooperative evolutionary code-optimisation agent skill. Supervisor, explorer, and reviewer roles can each be filled by any LLM through CLI, with candidates evolving on isolated git branches. Features interactive visualization and surfaces the winner as a pull request for human approval.
\end{itemize}}
}
